Is malaria control profitable? Return on investment of privately-managed residential fumigations at a large sugarcane processing facility in Southern Mozambique

### 2018-04-21 inst/rmd/02_methods.Rmd
externalities report

$\hat{Y}_{it}$ is the rate of absence. $\beta_{1}$ is the binary "season" variable, imputed from overall district clinical incidence. Our intervention is whether the residence of the worker in question was treated in the last year, and, if so, the time since treatment, represented, respectively, by $\beta_{2}$ and $\beta_{3}$. $\alpha_i$ reprsents the time invariant worker fixed effects, and $\delta_i$ represents the fixed effect of the particular malaria season. $\upsilon$ is the error term.

@@

>>>>

$\hat{Y}_{it}$ is the rate of absence. $\beta_{1}$ is the binary "season" variable, imputed from overall district clinical incidence. Our intervention is whether the residence of the worker in question was treated in the last year, and, if so, the time since treatment, represented, respectively, by $\beta_{2}$ and $\beta_{3}$. $\alpha_i$ represents the time invariant worker fixed effects, and $\delta_i$ represents the fixed effect of the particular malaria season. $\upsilon$ is the error term.

@@

### Externalities

One potential shortcoming of our analysis thus far is that a "control" worker (ie, one whose house has never been sprayed or was sprayed greater than one year ago) may actually be conferred some protection against malaria by the fumigations at his/her neighbors' houses. This positive spillover effect would theoretically go through two channels: (i) via a reduction of mosquitoes in the vicinity and (ii) via a reduction of the malaria parasite in the blood of humans in the vicinity (ie, the parasite "reservoir").

By the same token, just as being surrounded by IRS-treated homes may indirectly protect someone living in a home not treated by IRS, one might surmise that living on the periphery of the company grounds might lead to more malaria risk relative to living in the core, since homes near the periphery but outside of Maragra are less likely to be fumigated. In other words, to the extent that both positive and spillover effects are significant enough to warrant inclusion in our model, we would expect that (i) the prevalence of IRS in a worker's neighborhood should be associated with a reduction in absenteeism of the worker and (b) workers living further from the periphery of the company grounds should have lower absenteeism than workers living at the periphery. We test both of these hypotheses.

```{r}

```

### 2018-04-21 inst/rmd/03_results.Rmd
externalities report

```{r}
clean_up_model <- function(x){
  # extract coefficients
  coefs <- data.frame(coef(summary(x)))
  # use normal distribution to approximate p-value
  coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
  ps <- coefs$p.z
  x = broom::tidy(x)
  for(j in 2:(ncol(x) -1)){
    x[,j] <- x[,j] * 100
  }
  x$term <- gsub('seasonhigh', 'Malaria season', x$term)    
  x$term <- gsub('seasonlow', 'Low malaria season', x$term)
  x$term <- gsub('months_since', 'Months since IRS: ', x$term)
  x$term <- gsub('department', 'Department: ', x$term)
  x$term <- gsub('precipitation', 'Precipitation (mm) ', x$term)
  x$term <- gsub('maragra_fabricaTRUE', 'Living at factory', x$term)
  x$term <- gsub('sexM', 'Male', x$term)
  x$term <- gsub('permanent_or_temporaryTemporary', 'Temp contract', x$term)
  x$term <- gsub('rainyTRUE', 'Rainy day', x$term)
  x$term <- gsub('on_siteTRUE', 'On site', x$term)
  x$term <- gsub('on_siteFALSE', 'Off site', x$term)
  x$term <- gsub('fieldNot field worker', 'Not field worker', x$term)
  names(x) <- Hmisc::capitalize(names(x))
  names(x) <- gsub('.', ' ', names(x), fixed = TRUE)
  x$`P value` <- NA
  x$`P value`[1:length(ps)] <- ps
  x <- x %>% 
    mutate(Estimate = paste0(round(Estimate, 3), ' (P',
                             ifelse(`P value` <= 0.001,
                                    '<0.001',
                                    paste0('=', round(`P value`, 3))
                                    ), ')')) %>%
    dplyr::select(Term, Estimate)
  x <- x %>% filter(!grepl('sd_', Term))
  x <- x %>% filter(!grepl('10+', Term, fixed = TRUE))
  return(x)
}

make_models_table <- function(model_list, the_caption = "Models with worker fixed effects"){

  out_list <- list()
  for(i in 1:length(model_list)){
    message(i)
    this_model <- names(model_list)[i]
    the_model <- model_list[[which(names(model_list) == this_model)]]
    the_model <- clean_up_model(the_model)
    names(the_model)[2] <- this_model
    out_list[[i]] <- the_model
  }

  df <- out_list[[1]]
  namer <- names(df)[2]
  names(df)[2] <- 'Estimate'

  for(i in 2:length(out_list)){
    temp <- out_list[[i]]
    namer[i] <- names(temp)[2]
    names(temp)[2] <- 'Estimate'
    df <- bind_rows(df, temp)
  }

  library(kableExtra)
  breaker <- nrow(out_list[[1]])
  lengther <- length(out_list)
  breaks <- c(0, breaker * 1:(lengther))
  k <- kable(df, format = "latex", caption = the_caption, booktabs = T) %>%
    kable_styling()
  for (i in 1:(length(breaks)-1)){
    message(i)
    k <- k %>%
      group_rows(namer[i], 
                 breaks[i] + 1,
                 breaks[i] + breaker,
                 latex_gap_space = "1.5em") 
  }
  print(k)
}
```

@@

### Externalities

One potential shortcoming of our analysis thus far is that a "control" worker (ie, one whose house has never been sprayed or was sprayed greater than one year ago) may actually be conferred some protection against malaria by the fumigations at his/her neighbors' houses. This positive spillover effect would theoretically go through two channels: (i) via a reduction of mosquitoes in the vicinity and (ii) via a reduction of the malaria parasite in the blood of humans in the vicinity (ie, the parasite "reservoir").

By the same token, just as being surrounded by IRS-treated homes may indirectly protect someone living in a home not treated by IRS, one might surmise that living on the periphery of the company grounds might lead to more malaria risk relative to living in the core, since homes near the periphery but outside of Maragra are less likely to be fumigated. In other words, to the extent that both positive and spillover effects are significant enough to warrant inclusion in our model, we would expect that (i) the prevalence of IRS in a worker's neighborhood should be associated with a reduction in absenteeism of the worker and (b) workers living further from the periphery of the company grounds should have lower absenteeism than workers living at the periphery. We test both of these hypotheses.

>>>>

@@

## Externalities

Below are model results for the full protection model.

```{r, results = 'asis'}
make_models_table(model_list = protection_models, the_caption = "All absenteeism with herd immunity: model results")
```

### 2018-04-21 inst/rmd/paper.Rmd
externalities report

```{r}
source('paper_prepare.R')
irs$months_since <- irs$days_since %/% 30

# Define function for making season
make_season <- function(date){
  out <- ifelse(as.numeric(format(date, '%m')) %in% c(11:12, 1:3),
                   'Malaria season', 'Off season')
  out <- factor(out, levels = c('Off season', 'Malaria season'))
  return(out)
}
```

>>>>

```{r}
source('paper_prepare.R')
```

### 2018-04-21 inst/rmd/paper.tex
externalities report

This section is in progress. Looking at neighborhood effects,
core-periphery effects, etc.

>>>>

One potential shortcoming of our analysis thus far is that a ``control''
worker (ie, one whose house has never been sprayed or was sprayed
greater than one year ago) may actually be conferred some protection
against malaria by the fumigations at his/her neighbors' houses. This
positive spillover effect would theoretically go through two channels:
(i) via a reduction of mosquitoes in the vicinity and (ii) via a
reduction of the malaria parasite in the blood of humans in the vicinity
(ie, the parasite ``reservoir'').

By the same token, just as being surrounded by IRS-treated homes may
indirectly protect someone living in a home not treated by IRS, one
might surmise that living on the periphery of the company grounds might
lead to more malaria risk relative to living in the core, since homes
near the periphery but outside of Maragra are less likely to be
fumigated. In other words, to the extent that both positive and
spillover effects are significant enough to warrant inclusion in our
model, we would expect that (i) the prevalence of IRS in a worker's
neighborhood should be associated with a reduction in absenteeism of the
worker and (b) workers living further from the periphery of the company
grounds should have lower absenteeism than workers living at the
periphery. We test both of these hypotheses.

\paragraph{Neighborhood protective
effect}\label{neighborhood-protective-effect}

\todo{Working on this now}

\paragraph{Core-periphery difference}\label{core-periphery-difference}

\todo{Working on this now}
